Methodology for Assessing the State of the Practice for Domain X

### 2020-10-11 StateOfPractice/Methodology/Methodology.tex
fixed typos in Methodology document

\begin{enumerate}
\item What artifacts do current software projects produce?  \pmi{keep}
\item What are the attitudes and actions of research software developers and toward:
\begin{enumerate}
\item sustainability?
\item usability?
\item modifiability? \pmi{think about and possibly remove this one}
\end{enumerate} \pmi{keep} \wss{What are we hoping to learn from this question?
  This might be a question for Olu, since she currently has the same research question.}
\item For a given domain of research software, what current projects provide the
  best examples of high quality software and documentation? \wss{Reworded
    version of one of Olu's research questions.}
\end{enumerate}

@@

\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather empirical measures found in Section \ref{SecEmpiricalMeasures}.
	\item Status - The software cannot be marked as incomplete or in an initial development phase.
\end{enumerate}

>>>>

\begin{enumerate}
\item What artifacts do current software projects produce?  \pmi{keep}
\item What are the attitudes and actions of research software developers toward:
\begin{enumerate}
\item sustainability?
\item usability?
\item modifiability? \pmi{think about and possibly remove this one}
\end{enumerate} \pmi{keep} \wss{What are we hoping to learn from this question?
  This might be a question for Olu, since she currently has the same research question.}
\item For a given domain of research software, what current projects provide the
  best examples of high quality software and documentation? \wss{Reworded
    version of one of Olu's research questions.}
\end{enumerate}

@@

\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather empirical measures found in Section \ref{SecEmpiricalMeasures}.
	\item The software cannot be marked as incomplete or in an initial development phase.
\end{enumerate}
